### 2021-03-11 results/draft.tex
added the explanation about correlation method

\ \ \ \ \ \ \ \ \ \ 
Although each methods estimate the spatial distribution of species using multiple data sets, we need to select method depending on the data features for analysis because there are strengths and weaknesses (Pacifici et al. 2017; Miller et al. 2018). The joint likelihood method may be problematic when the added data (second data?) is of poorly quality compared to correlation and covariate methods because each data can directly inform the latent occurrence state and the weight given to estimate the parameters is naturally determined by their relative size and quality. Thus, it is not the best method when our second data is low quality while it is the best method when all data are deemed reliable.
%The joint likelihood method simultaneously fits a likelihood to both data sources
%The joint likelihood approach uses multiple data types to simultaneously estimate a shared set of parameters.
%the shared set of parameters within each of the individual likelihoods is constrained to be equal across likelihoods.

>>>>

\ \ \ \ \ \ \ \ \ \ 
Although each methods estimate the spatial distribution of species using multiple data sets, we need to select method depending on the data features for analysis because there are strengths and weaknesses (Pacifici et al. 2017; Miller et al. 2018). The joint likelihood method may be problematic when the second data is of poorly quality compared to correlation and covariate methods because each data can directly inform the latent occurrence state (probabilities?) and the weight given to estimate the parameters is naturally determined by their relative size and quality. Thus, it is not the best method when our second data is low quality while it is the best method when our second data is high quality (vise versa). 
%The joint likelihood method simultaneously fits a likelihood to both data sources
%The joint likelihood approach uses multiple data types to simultaneously estimate a shared set of parameters.
%the shared set of parameters within each of the individual likelihoods is constrained to be equal across likelihoods.
The correlation method is added robustness to the joint likelihood because the second data indirectly inform the occurrence state. Thus, it is the best method when our second data is low quality while it is inferior to the joint likelihood method when both data are deemed reliable.
%The correlation method is added robustness to the joint likelihood for the influence of unreliable data because the second data indirectly inform the occurrence state.
% while this method is inferior to the joint likelihood when both data are deemed reliable.
